In-silico molecular enrichment and clearance of the human intracranial space

### 2025-06-20 paper/main.tex
Attempt to answer Reviewer #1

% Limitations
In terms of limitations, our primary constraint modelling-wise is the
geometric representation of the vascular (and therefore also
perivascular) networks. Concretely, we account for no vessels below
the original MRI resolution limits, and thus only a part of the
cerebral surface vasculature and effectively not the cortical
vessels. In addition, and again due to lack of resolution, there is
uncertainty associated with the location of the vessel segments
relative to the CSF spaces and parenchyma, with some vessels
surrounded by both domains and some vessels completely entering the
parenchyma before returning to the SAS. Higher resolution MRI data
(T1w and e.g. time-of-flight, QSM or other modalities) in more
subjects would immediately allow for more detailed studies of this
aspect. As a result of the lack of an accurate representation of the
cortical and subcortical white matter vasculature, we have considered
a basic transport model within the parenchyma, modelling extracellular
diffusion alone. To compensate, we have focused on reporting detailed
predictions in the CSF spaces and surface PVS after not more than 24
hours. In particular, we note that, we observe tracer accumulation at
the perivascular network ends after 12 hours, similar to that
previously observed for microspheres~\cite{bedussi2018paravascular,
  mestre2018flow}, which here can be interpreted as an artifact of the
incomplete network creating a barrier for tracer movement. Previously,
by inferring transport parameters within the human brain from
glymphatic MRI data, we have found that molecular transport within the
parenchyma is well-represented by $\approx 3\times$ enhanced diffusion
augmented by local clearance e.g.~across the blood-brain barrier, or
by diffusion-convection with a complex pattern of spatially-varying
interstitial fluid flow on the order of 1-10 \textmu
m/min~\cite{vinje2023human}. We will incorporate such transport
mechanisms within the parenchyma in future work. Finally, we also note
that we simulate the intracranial distribution of a tracer
concentration appearing at the craniocervical junction rather than as
an intrathecal injection. We thus neglect absorption of both CSF and tracer in the spinal compartment, and therefore overestimate the amount of
tracer entering into the intracranial spaces; however, due to the
linearity of the mathematical model, it is valid to directly interpret
the in-silico concentrations relative to the total amount of tracer.

>>>>

% Limitations
In terms of limitations, our primary constraint modelling-wise is the
geometric representation of the vascular (and therefore also
perivascular) networks. Concretely, we account for no vessels below
the original MRI resolution limits, and thus only a part of the
cerebral surface vasculature and effectively not the cortical
vessels. In addition, and again due to lack of resolution, there is
uncertainty associated with the location of the vessel segments
relative to the CSF spaces and parenchyma, with some vessels
surrounded by both domains and some vessels completely entering the
parenchyma before returning to the SAS. Higher resolution MRI data
(T1w and e.g. time-of-flight, QSM or other modalities) in more
subjects would immediately allow for more detailed studies of this
aspect. As a result of the lack of an accurate representation of the
cortical and subcortical white matter vasculature, we have considered
a basic transport model within the parenchyma, modelling extracellular
diffusion alone and zero bulk interstitial fluid flow. To compensate, we have focused on reporting detailed
predictions in the CSF spaces and surface PVS after not more than 24
hours. In particular, we note that, we observe tracer accumulation at
the perivascular network ends after 12 hours, similar to that
previously observed for microspheres~\cite{bedussi2018paravascular,
  mestre2018flow}, which here can be interpreted as an artifact of the
incomplete network creating a barrier for tracer movement. Previously,
by inferring transport parameters within the human brain from
glymphatic MRI data, we have found that molecular transport within the
parenchyma is well-represented by $\approx 3\times$ enhanced diffusion
augmented by local clearance e.g.~across the blood-brain barrier, or
by diffusion-convection with a complex pattern of spatially-varying
interstitial fluid flow on the order of 1-10 \textmu
m/min~\cite{vinje2023human}. We will incorporate such transport
mechanisms within the parenchyma in future work. Finally, we also note
that we simulate the intracranial distribution of a tracer
concentration appearing at the craniocervical junction rather than as
an intrathecal injection. We thus neglect absorption of both CSF and tracer in the spinal compartment, and therefore overestimate the amount of
tracer entering into the intracranial spaces; however, due to the
linearity of the mathematical model, it is valid to directly interpret
the in-silico concentrations relative to the total amount of tracer.
